Language Bias in a Multilingual Tweet Corpus

### 2018-05-17 paper.tex
Comments

This paper presents a multilingual tweet collection with some analysis of users, language use and content. The analysis reveals that geo-location and a limited list of Twitter users leads to a biased collection.
%
% the resource might be used in several areas ranging from computational linguistics, information retrieval and social science.
%
The challenges of building representative and complete tweet collection are:
\begin{itemize}
\item How the content of users who do not engage with media accounts (newspapers, radio stations, etc.~\ldots) might be collected respecting their privacy and not introducing bias into the collection?
\item How to get hints of what topics are more popular among ``minorities''? What are tweets in Russian and English are about?
\item Some tweets are multilingual. How can code-switching be detected reliably?
\end{itemize}

>>>>

This paper presents a multilingual tweet collection with some analysis of users, language use and content. The analysis revealed differences in language use between the geo-located collection, global collection and topical sub-collections.

However, the question of whether the collection is any good remains open. It would be easy to test its extrinsic properties, for example, whether it leads to improvements in a language identification system when used as training data. But does not reveal its intrinsic properties.

%The challenges of building representative and complete tweet collection are:
%\begin{itemize}
%\item How the content of users who do not engage with media accounts (newspapers, radio stations, etc.~\ldots) might be collected respecting their privacy and not introducing bias into the collection?
%\item How to get hints of what topics are more popular among ``minorities''? What are tweets in Russian and English are about?
%\item Some tweets are multilingual. How can code-switching be detected reliably?
%\end{itemize}
